\documentclass[11pt, a4paper, oneside]{exam}
\usepackage[margin=3cm]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{MnSymbol}
\usepackage{appendix}
\usepackage{graphicx}

\theoremstyle{definition}\newtheorem{define}{Definition}[section]
\theoremstyle{remark}\newtheorem{remark}{Remark}
\theoremstyle{definition}\newtheorem{example}{Example}[subsection]
\theoremstyle{definition}\newtheorem{notation}{Notation}[section]
\theoremstyle{definition}\newtheorem{theorem}{Theorem}[section]
\theoremstyle{definition}\newtheorem{corollary}{Corollary}[section]


\title{asdf}
\author{Name
}
\date{}

\begin{document}
\begin{questions}
\section{Problem Set}

\question[1]
Write down the converse of the following statement:

If it is raining then the floor will be wet.

\question
Write down the negation of the following statements:
\begin{parts}
  \part[1] The city of Toronto is not in Australia.
  \part[2] If the weather is good then I will be at the beach.
  \part[2] Any multiple of an even number is even. (hint: convert this to symbols first)
\end{parts}

\question[1] 
Write down the contrapositive of the following statement:

A square has an angle sum of $360^\circ$.

\question[1]
Write down the two converse statements equivalent to the following statement:

A number is even if and only if it has a remainder of 0 when divided by 2.

\question[2] Prove that the sum of three consecutive odd integers is divisible by 3.

\question[2] Prove that a positive integer that ends in 325 cannot be the square of an integer.

\question[2] By proving the contrapositive, prove for an integer $n$ that if $n^2-1$ is not divisible by 3 then $n$ is divisible by 3.

\question
\begin{parts}
  \part[2] Show by expanding that 

\[x^n -1 = (x-1)(x^{n-1} + x^{n-2} + x^{n-3} + \ldots + x^2 + x + 1) \]

  \part[2] By proving the contrapositive, prove that if $2^n - 1$ is a prime number, then $n$ is also prime.
  \part[2]Give a counter-example of the converse.
\end{parts}

\question[2] Prove that for an integer $n$, if $n^2 - 6n + 5$ is even then $n$ is odd.

\question[2] Prove that $\cos^2(5^\circ)$ is irrational. Hint: You are given that $\cos 3\theta = 4\cos^3\theta - 3\cos\theta$.

\question[2] Prove that if $n$ is a composite integer, then it has a prime divisor less than or equal to $\sqrt{n}$.

\question[3] Prove by induction \[ \sum_{r=1}^n r(3r-1) = n^2(n+1) \]

\question[4] A sequence is recursively defined by $a_1 = 3$ and $a_n = 2a_{n-1} - 1$ for $n >1$. Prove by induction that $a_n = 2^n + 1$.\\

\question[3] Prove by induction for all positive integers $n$ that $5^n + 2\times11^n$ is divisible by 3.

\question[3] Prove by induction $n! > 2^n$ for integers $n\geq 4$.

\question
\begin{parts}
  \part[1] Prove that $x^2+y^2 \geq 2xy$ for $x,y>0$.
  \part[2] Hence, prove if $a^2 + b^2 = c^2 + d^2 = 1$, then $ac + bd \leq 1$.
\end{parts}

\question[3] By using the AM-GM inequality, show that for all positive integers $n$, 
\[ n! \leq \left(\frac{n+1}{2}\right)^n \]


\question The $x$ and $y$ coordinates of three points $A$, $B$ and $C$ in a number plane are all positive integers.
\begin{parts}
  \part[2] Show that the area of $\triangle ABC$ is rational.
  \part[2] Hence, show that $\triangle ABC$ cannot be an equilateral triangle.
\end{parts}

\question[2]

[Russell's Paradox]

Let $R$ be the set of all sets that are not members of themselves.

Show that $R\in R$ if and only if $R \not\in R$.





% ------------------------------------------------------------------------------
\end{questions}
\end{document}

% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------


